---
title: "report"
author: "Ignacio Medina de Andrés"
date: "19/3/2021"
output: html_document
params: 
  selAge: 25
  selWage: 50
  selSpeed: 50
  selControl: 50
  selDribbling: 50
  selPass: 50
  selLPass: 50
---

```{r include=FALSE}
model_price <- lm(Price ~ Age+Wage+Speed+Control++Dribbling+ShortPassing+LongPassing,data=df)

price <- summary(model_price)$coef[1,1] + 
      summary(model_price)$coef[2,1]*params$selAge + summary(model_price)$coef[3,1]*params$selWage + 
      summary(model_price)$coef[4,1]*params$selSpeed + summary(model_price)$coef[5,1]*params$selControl +
      summary(model_price)$coef[6,1]*params$selDribbling + summary(model_price)$coef[7,1]*params$selPass +
      summary(model_price)$coef[8,1]*params$selLPass
```

This final player signing price estimation has been computed by tuning its physical and technical stats, obtained from the **FIFA** (Fédération Internationale de Football Association) stats assigned for the 2019/20 season. 

After tuning these player stats, the **estimated signing price** for a player with the following characteristics: 

- `r params$selAge` years old, 
- earning `r params$selWage` € per year, 
- `r params$selSpeed` of speed rating, 
- `r params$selControl` of ball control rating, 
- `r params$selDribbling` of dribbling rating, 
- `r params$selPass` of short pass rating, 
- and `r params$selLPass` of finishing skills 

would be:

```{r echo=FALSE}
cat(round(price,2),"€")
```


### Linear model behind the signing price estimation 

```{r echo=FALSE}
summary(model_price)
```



